Evolutionary Learning of Policies for MCTS Simulations

### 2012-03-24 thesis/paper/paper.tex
Changed 13x13 figures to 7x7 for better visibility. Larger fonts on the weight-pattern-map figure.

\section{Background: The Game of Hex}
\label{s:hex}
Hex is a two player, full-information, abstract strategy game played on an $N$x$N$ grid of hexagons. The players are \hblack{} and \hwhite{} and alternate placing markers of their color on empty hexagons. 
The object of the game is to form an unbroken chain from one side of the board to the other. 
Figure \ref{fig:13x13inprogress} shows an example game in progress on a 13x13 board, note that the numbers indicate
the order in which the markers were played and have no effect on the game.
Figure \ref{fig:13x13finished} shows the final position, \hblack{} having just played the winning move (71), completing an unbroken chain connecting both his sides.

@@

\begin{figure}[tb]
\resizebox{3.35in}{!}{	\begin{HexBoard}[board size=13]
		\HGame{c4,f6,e11,i8,h8,i1,i6,d5,i3,h9,h5,h4,i4,g9,f9,g8,f7,f8,e8}
	\end{HexBoard}
	}
	\caption{13x13 Hex Game, \hwhite{} to play.}
	\label{fig:13x13inprogress}
\end{figure}

\begin{figure}[tb]
\resizebox{3.35in}{!}{	\begin{HexBoard}[board size=13]
		\HGame{c4,f6,e11,i8,h8,i1,i6,d5,i3,
				   h9,h5,h4,i4,g9,f9,g8,f7,f8,
				   e8,e9,c10,k8,c9,g6,g7,c11,
				   d10,h6,h7,i5,j5,j4,k4,k3,
				   m2,l3,m3,l4,c6,e11,l5,m4,
				   d11,b7,e6,d12,c12,c7,e7,f5,
				   e5,d9,d8,f4,e4,f3,a2,e3,d6,
				   c3,d3,d4,b5,e2,d2,d1,e1,b13,
				   c13,c5,b6}
	\end{HexBoard}
	}
	\caption{Finished 13x13 Hex Game, \hblack{}'s play 71 (at \loc{b6}) gives him an unbroken path from top to bottom.}
	\label{fig:13x13finished}
\end{figure}

>>>>

\section{Background: The Game of Hex}
\label{s:hex}
Hex is a two player, full-information, abstract strategy game played on an $N$x$N$ grid of hexagons. The players are \hblack{} and \hwhite{} and alternate placing markers of their color on empty hexagons. 
The object of the game is to form an unbroken chain from one side of the board to the other. 
Figure \ref{fig:inprogress} shows an example game in progress on a 7x7 board, note that the numbers indicate
the order in which the markers were played and have no effect on the game.
Figure \ref{fig:finished} shows the final position, \hblack{} having just played the winning move (25), completing an unbroken chain connecting both his sides.

@@

\begin{figure}[tb]
\resizebox{3.3in}{!}{	\begin{HexBoard}[board size=7]
		\HGame{d4,d3,e3,f1,c2,d6,b5,e2}
	\end{HexBoard}
	}
	\caption{7x7 Hex Game, \hwhite{} to play.}
	\label{fig:inprogress}
\end{figure}

\begin{figure}[tb]
\resizebox{3.3in}{!}{	\begin{HexBoard}[board size=7]
		\HGame{d4,d3,e3,f1,c2,d6,b5,e2,c4,c3,a4,b6,c6,c5,d5,b7,c7,b4,a5,b3,a3,b1,b2,c1,d1}
	\end{HexBoard}
	}
	\caption{Finished 7x7 Hex Game, \hblack{}'s play 25 (at \loc{d1}) gives him an unbroken path from top to bottom.}
	\label{fig:finished}
\end{figure}
